---
title: "Statistical Inference Course Project"
author: "RogierGit"
output: word_document
---

# 1 Overview
We will investigate the exponential distribution using lambda = 0.2. 

# 2. Setup
## Setting up environment
```{r, message=FALSE, error=FALSE, warning=FALSE, results="hide"}
# Set the seed
set.seed(1234)

# Packages
library(knitr)

```

# 3. Simulations

# The theoretical mean of the exp distribution
The theoretical mean of the exponential distribution is 1/lamba. For our analysis in which we use lambda = 0.2, this means that the theoretical mean is:  
```{r}
# Theoretical mean:
theoreticalmean <- 1/0.2
```

# The theoretical standard deviation of exp distribution
The theoretical standard deviation of the exponential distribution is 1/lambda. Here we also use lambda = 0.2, which gives us a theoretical sd of:  

```{r}
# Theoretical standard deviation:
theoreticalsd <- 1/0.2

# The theoretical variance:
theoreticalsd^2
```

# A distribution of single set of 40 random exponentials
```{r}
# Create a vector with 40 random exponentials
single_exp <- rexp(40, 0.2) #0.2 = lambda

# Mean of the exponentials
(single_exp_mean <- mean(single_exp))

# Variance of the exponentials to the mean
(single_exp_var <- var(single_exp))

# Standard deviation for the single sample
# Variance of the exponentials to the mean
(single_exp_sd <- sd(single_exp))

```

# Running 1000 simulations
```{r}
# Run 1000 simulations of a vector of 40 random exponentials and store the mean
sim_exp_means = NULL

for (i in 1 : 1000) sim_exp_means = c(sim_exp_means, mean(rexp(40, 0.2)))

# Mean of the means from the 1000 exponential simulations
(mean_of_sim_exp_means <- mean(sim_exp_means))

```

# 4. Sample Mean versus Theoretical Mean
We start by comparing the results of the single sample to the theoretical mean
```{r}
hist(single_exp, xlab="Exponentials", main=NULL, breaks=10)
abline(v = theoreticalmean, lwd = 2, col="green")
abline(v = single_exp_mean, lwd = 2, col="blue")
legend("topright", pch=1, col=c("green", "blue"), legend=c("Theoretical mean", "Single sample mean"))
title("Single sample of 40 exponentials")
```

We compare the sample means from the 1000 simulations 
```{r}

hist(sim_exp_means, xlab="Simulation means", main=NULL, breaks=40)
abline(v = theoreticalmean, lwd = 2, col="green")
abline(v = mean_of_sim_exp_means, lwd = 2, col="blue")
legend("topright", pch=1, col=c("green", "blue"), legend=c("Theoretical mean", "Simulation mean"))
title("Means of 1000 simulations")
```

From the plot we cannot distinquish the theoretical and the simulation mean. The simulation means is approaching the theoretical mean.
```{r}
#Theoretical mean
theoreticalmean

#Simulation mean
mean_of_sim_exp_means
```



# 5. Sample Variance versus Theoretical Variance
Variance is the square distance from the mean 



# 6. Distribution
Explain how one can tell the distribution is approximately normal.






Regarding the distribution of the mean of 40 exponentials. Did the student show where the distribution is centered at and compare it  to the theoretical center of the distribution?

Regarding the distribution of the mean of 40 exponentials. Did the student show how variable it is and compare it to the theoretical variance of the distribution?

Was the report a pdf report of the required length?

Here's your opportunity to give this project +1 for effort. Did the student basically try to answer the question?
